Appendix A: Stochastic simulations of noisy phenomena

### 2017-11-01 appendixA/appendixA.Rmd
streamline font setup?

```{r echo=FALSE, cache=FALSE, eval=TRUE}
## plot themes, non-essential. Comment out if theme creates trouble with fonts on your system.
library(Cairo)
library(hrbrthemes)
library(extrafont)

>>>>

```{r echo=FALSE, cache=FALSE, eval=TRUE}
## plot themes, non-essential. Comment out if theme creates trouble with fonts on your system.
library(Cairo)
library(hrbrthemes)
library(extrafont)
#extrafont::font_import(prompt=FALSE)    # One-time use to set up fonts, can be slow.

## One-time setup
hrbrthemes::import_roboto_condensed()   # One-time use to set up fonts 
d <- read.csv(extrafont:::fonttable_file(), stringsAsFactors = FALSE)
d[grepl("Light", d$FontName), ]$FamilyName <- "Roboto Condensed Light"
write.csv(d, extrafont:::fonttable_file(), row.names = FALSE)

#extrafont::font_import(prompt=FALSE)    # One-time use to set up fonts, can be slow.
#hrbrthemes::import_roboto_condensed()   # One-time use to set up fonts
